
```{r}
library("rstan", quietly = T)
library("tidyverse", quietly = T)
library("magrittr", quietly = T)

##this is where the data is
URL <- "https://raw.githubusercontent.com/carlislerainey/priors-for-separation/master/br-replication/data/need.csv"
```

```{r}
##sy: this function automatically centers covariates.  rstanarm has this function built into it already
autoscale <- function(x, center = TRUE, scale = TRUE) {
  nvals <- length(unique(x))
  if (nvals <= 1) {
    out <- x
  } else if (nvals == 2) {
    out <- if (scale) {
      (x - min(x, na.rm = TRUE)) / diff(range(x, finite = TRUE))
    } else x
    if (center) {
      out <- x - mean(x)
    }
  } else {
    out <- if (center) {
      x - mean(x, na.rm = TRUE)
    } else x
    out <- if (scale) out / sd(out, na.rm = TRUE)
  }
  out
}


```

###Define model
```{r}



f <- (oppose_expansion ~ dem_governor + obama_win + gop_leg + percent_uninsured +
        income + percent_nonwhite + percent_metro)
```

### Get data and set up 
```{r}
br <- read_csv(URL) %>%
  mutate(oppose_expansion = 1 - support_expansion,
         dem_governor = -1 * gop_governor,
         obama_win = as.integer(obama_share >= 0.5),
         percent_nonwhite = percent_black + percent_hispanic)%>%
  rename(gop_leg = legGOP) %>%
  # keep only variables in the formula
  model.frame(f, data = .) %>%
  # drop missing values (if any?)
  drop_na()

```
use the centering/standardizing function
```{r}
br_scaled <- br %>%
  # Autoscale all vars but response
  mutate_at(vars(-oppose_expansion), autoscale)
```

Run the simple GLM
```{r}
glm(f, data = br, family = "binomial") %>% summary()
```
Run the rstanarm model.  This is a built in function that has a default prior.  It automatically adjusts scale 
```{r}
library("rstanarm")  ##sy: has some stan glm functions
fit1<-stan_glm(f, data = br, family = "binomial")
fit2<-stan_glm(f, data = br, prior = NULL, family = "binomial")

summary(fit1)
help("prior_summary")
```
The GLM version includes priors, so the uncertainty decreases from the regular glm model



```{r}
library(bayesplot, quietly=T)
##fit1 had the prior
mcmc_dens(as.array(fit1), "dem_governor")

##fit2 ran w/o prior
mcmc_dens(as.array(fit2), "dem_governor")

```
The model w/o prior has much more extreme values and a larger distribution overall

